--
title: "Prevalence of C469Y mutations in Agago"
author: "Kisakye"
date: "`r Sys.Date()`"
output:
html_document:
df_print: paged
toc: yes
highlight: tango
number_sections: no
theme: sandstone
code_folding: hide
toc_depth: 1
toc_float: yes
---

```{r cleanup, warning=FALSE, message=FALSE, error=FALSE}
# CLEANUP
# Clear all variables:
rm(list=ls(all=TRUE))
# Unload current packages:
 if (!is.null(names(utils::sessionInfo()[["otherPkgs"]]))) pacman::p_unload("all")
```


```{r packages, results="hide", warning=FALSE, message=FALSE, error=FALSE}
# LOAD PACKAGES:
library(magrittr)
library(dplyr)
library(tidyr)
```


# Load data
```{r}
# dr_data1 <-read.table("/home/diana/Trainings/resmarkers_haplotype_summary.txt", sep = '\t')

dr_data2 <-read.table("~/Trainings/Malaria-genomics/data/CopyOfresmarkers_summary.txt", header = TRUE, sep = "\t", stringsAsFactors = F, na.strings = " ")  # make sure to replace missing values with empty strings


```

# Select mutation of interest 
```{r}
# Look at the names of the dataset to identify mutation of interest
names(dr_data2)

# Select a subset of the dataframe for the mutation of interest
dr_kelch <- dr_data2 %>%
                dplyr::select("SampleName",  "PF3D7_1343700.k13.469")%>% 
# sum(is.na(dr_kelch$PF3D7_1343700.k13.469)) # 15 samples have missing values, lets remove them.
                na.omit()

```

```{r}
# Split genotypes and the reads
dr_kelch2 <-dr_kelch %>%
 mutate(gt = stringr::str_split( PF3D7_1343700.k13.469, " ()", simplify = TRUE)[,1]) %>% 
  mutate(reads = stringr::str_split( PF3D7_1343700.k13.469, " ()" , simplify = TRUE)[,2])
 
```

# Create a dataframe with WT, Mutant and Mixed genotypes
```{r}
dr_kelch3 <- dr_kelch2 %>%
  mutate(Mixed =ifelse(gt == "Cys,Tyr", 1, 0)) %>%
  mutate(Wildtype = ifelse(gt == "Cys", 1, 0)) %>%
  mutate(Mutant =ifelse( gt == "Tyr", 1, 0 ))

```

# Calculate the prevalence of the different genotypes
```{r}
dr_kelch3%>%
  summarise(prev_Wildtype = mean(Wildtype),
            prev_Mutant = mean(Mutant),
            prev_Mixed = mean(Mixed))


```

## Session info  
<button class="button" onclick="myFunction('DIV_5')">Show/hide session info</button>
  <div id="DIV_5" class="div_default_hide">
  
```{r print_date_and_time}
Sys.time()
```

```{r print_session_info}
# sessionInfo()
devtools::session_info()
```
</div>
  
  <script>
  var divsToHide = document.getElementsByClassName("div_default_hide");
for(var i = 0; i < divsToHide.length; i++)
{
  divsToHide[i].style.display = 'none';
}
</script>